---
title: "Untitled"
output: html_document
date: "2025-03-04"
---


## Description

The goal is to match survey respondents who (a) directly observe and collect data, or (b) just directly observe kelp forests to specific kelp forests sites or areas, rather than just counties. 

This script takes a look at which individuals and organizations are represented in the survey data v. those with publicly available data on monitoring or restoration sites. 

Key sources of information:

[Sanctuary Integrated Monitoring Network Map](https://csumb.maps.arcgis.com/apps/webappviewer/index.html?id=f555c42a349444f2942900139f88fe34)

[Kelp Forest Challenge](https://kelpforestalliance.com/kelp-forest-challenge)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Set up  -----------------------------------------------------------------

library(readr)
library(tidyverse) 
library(dplyr) 
library(tidyr) 
library(here)
library(magrittr)
library(janitor)
#

sn.dir <- here('confidential_data')
```

## Data

this is the raw survey data
```{r}
dat_survey <- read_csv(here(sn.dir, "raw", "kelp_jan.9.25_copy.csv"))[-c(1,2),]
dat_survey %<>% clean_names()
```

this is the cleaned up social network
```{r}
sn <- read_csv(here(sn.dir, 'processed', 'cleaned_social_network_with_org_2025-02-28.csv'))
```

this is the cleaned up data set on the answer to the question: What are the main ways you learn about kelp forest-related issues?
```{r}
info <- read_csv(here(sn.dir, 'processed','cleaned_responseID_by_info_source_q9.csv'))
```

these are the organizations represented in the online map data or by DISES members / partners:
```{r}
kms_map <- c('Channel Islands National Marine Sanctuary', 
             'Humboldt State University','Reef Check', 
             'Vantuna Research Group', 'Occidental College - Vantuna Research Group', 
             'University of California Santa Barbara', 'University of California Santa Barbara - Marine Science Institute',
             'PISCO','Partnership for Interdisciplinary Studies of Coastal Oceans')

kfp_map <- c('The Nature Conservancy','Get Inspired', 'The Bay Foundation')

dises <- c('University of California Davis','University of California Santa Cruz','California State Polytechnic University Humboldt')

dises_partner <- c('California Department of Fish and Wildlife', 'Reef Check','Greater Farallones Association', 'Greater Farallones National Marine Sanctuary','Monterey Bay National Marine Sanctuary')
```


*are all response IDs / orgs in the social network in the info data frame, and vice versa?* Not sure why so many are missing from the social network data frame. work with only the info data frame in this script. 
```{r}
missing_from_sn <- info$response_id[which(!(info$response_id %in% sn$response_id))]
length(missing_from_sn)

missing_from_info <- sn$response_id[which(!(sn$response_id %in% info$response_id))]
length(missing_from_info)


# View(dat_survey %>% filter(response_id %in% missing_from_sn))
```


## Direct observers

Get a list of those who (a) directly observe and collect data, or (b) just directly observe kelp forests. These should be mutually exclusive lists.
```{r echo=FALSE}
do1 <- info %>%
  group_by(response_id) %>%
  summarise(all_info=paste(info_type,collapse=",")) %>%
  filter(grepl('I directly observe conditions', all_info) & grepl('I collect or analyze data', all_info)) %>%
  dplyr::select(response_id) %>%
  # left_join(sn, by='response_id') %>%
  left_join(dplyr::select(dat_survey, response_id, recipient_first_name, recipient_last_name) %>% distinct())


do2 <- info %>%
  group_by(response_id) %>%
  summarise(all_info=paste(info_type,collapse=",")) %>%
  filter(grepl('I directly observe conditions', all_info) & !(grepl('I collect or analyze data', all_info))) %>%
  dplyr::select(response_id) %>%
  # left_join(sn, by='response_id') %>%
  left_join(dplyr::select(dat_survey, response_id, recipient_first_name, recipient_last_name) %>% distinct())


any(do1$response_id %in% do2$response_id)

paste0('Observe and Data: ',length(unique(do1$response_id)))
paste0('Observe only: ', length(unique(do2$response_id)))
```

### Observe & Data

Which organizations are represented by DO1s?
```{r}
unique(do1$org_name)
```

What proportion of organizations, respondents are on the kelp monitoring map or in the DISES group?
```{r echo=FALSE}
do1_summary <- do1 %>% mutate(avail=ifelse(org_name %in% kms_map, 'KMS Map',
                                           ifelse(org_name %in% kfp_map, 'KelpChallenge Map',
                                           ifelse(org_name %in% dises, 'DISES',
                                                  ifelse(org_name %in% dises_partner, 'DISES partner', NA)))))
```
```{r}
paste0('Individuals: ',
length(unique(filter(do1_summary, !is.na(avail))$response_id))/length(unique(do1_summary$response_id)))

paste0('Organizations: ',
       round(length(unique(filter(do1_summary, !is.na(avail))$org_name))/length(unique(do1_summary$org_name)), 3))
```


Which of these organizations are *not* on the kelp monitoring/challenge map or in the DISES group?
```{r echo=FALSE}
unique(do1_summary %>% filter(is.na(avail)) %>%
  pull(org_name))
```

Who are the individuals?
```{r}
do1_summary %>%
  filter(is.na(avail)) %>%
  filter(is.na(org_name) | org_name=="Individual") %>%
  dplyr::select(response_id, org_name) %>%
  left_join(dplyr::select(dat_survey, finished, response_id, recipient_first_name, recipient_last_name) %>% distinct()) %>%
  filter(finished=='True') %>% distinct()
```

Who do they work with? This won't be an exhaustive list because some are missing from the social network. 
```{r}
do1_summary %>%
  filter(is.na(avail)) %>%
  filter(is.na(org_name) | org_name=="Individual") %>%
  dplyr::select(response_id, org_name) %>%
  left_join(dplyr::select(dat_survey, finished, response_id, recipient_first_name, recipient_last_name) %>% distinct()) %>%
  filter(finished=='True') %>% distinct() %>%
  left_join(dplyr::select(sn, response_id, alter), by='response_id') %>%
  dplyr::select(-finished) %>%
  unite(col='recipient_name', recipient_first_name, recipient_last_name, sep=" ")
```


Save to a spreadsheet. 
```{r}
```





### Just Observe


Which organizations are represented by DO2s?
```{r}
unique(do2$org_name)
```

What proportion of organizations, respondents are on the kelp monitoring map or in the DISES group?
```{r echo=FALSE}
do2_summary <- do2 %>% mutate(avail=ifelse(org_name %in% kms_map, 'KMS Map',
                                           ifelse(org_name %in% dises, 'DISES',
                                                  ifelse(org_name %in% dises_partner, 'DISES partner', NA)))) %>%
  mutate(inDO1 = ifelse((!is.na(org_name) & org_name != "Individual" & org_name %in% do1$org_name), 'y','n'))


paste0('Individuals: ',
length(unique(filter(do2_summary, !is.na(avail))$response_id))/length(unique(do2_summary$response_id)))

paste0('Organizations: ',
       round(length(unique(filter(do2_summary, !is.na(avail))$org_name))/length(unique(do2_summary$org_name)), 3))
```

What organizations are not accounted for?
```{r}
unique(do2_summary %>% filter(is.na(avail)) %>% pull(org_name))
```

What organizations that are not accounted for, are also in the DO1 group?
```{r}
unique(do2_summary %>% filter(is.na(avail)) %>% filter(inDO1=='y') %>% pull(org_name))
```

Who are the individuals?
```{r}
do2_summary %>%
  filter(is.na(avail)) %>%
  filter(is.na(org_name) | org_name=="Individual") %>%
  dplyr::select(response_id, org_name) %>%
  left_join(dplyr::select(dat_survey, finished, response_id, recipient_first_name, recipient_last_name) %>% distinct()) %>%
  filter(finished=='True') %>% distinct()
```

Who do they work with? This won't be an exhaustive list because some are missing from the social network. 
```{r}
do2_summary %>%
  filter(is.na(avail)) %>%
  filter(is.na(org_name) | org_name=="Individual") %>%
  dplyr::select(response_id, org_name) %>%
  left_join(dplyr::select(dat_survey, finished, response_id, recipient_first_name, recipient_last_name) %>% distinct()) %>%
  filter(finished=='True') %>% distinct() %>%
  left_join(dplyr::select(sn, response_id, alter), by='response_id') %>%
  dplyr::select(-finished) %>%
  unite(col='recipient_name', recipient_first_name, recipient_last_name, sep=" ")
```







## Other info sources

What proportion of survey respondents in the social network aren't direct observers?
```{r}
ndo <- info %>%
  group_by(response_id) %>%
  summarise(all_info=paste(info_type,collapse=",")) %>%
  filter(!(grepl('I directly observe conditions', all_info))) %>%
  dplyr::select(response_id) %>%
  # left_join(sn, by='response_id') %>%
  left_join(dplyr::select(dat_survey, response_id, recipient_first_name, recipient_last_name) %>% distinct())

length(unique(ndo$response_id)) / length(unique(info$response_id))
```

How many organizations are represented by people in this category?
```{r}
unique(ndo$org_name)
```

Do these people represent new organizations, or the same organizations as the direct observers?
```{r}
unique(ndo$org_name[which(!(ndo$org_name %in% c(do1$org_name, do2$org_name)))])
```


