---
title: "Identify sub-county locales for direct observers"
output: 
  html_document:
    toc: yes
    toc_float: yes
---

**author: Mary Fisher**

**date written: 2025-03-04**



## Description

The goal is to match survey respondents who (a) directly observe and collect data, or (b) just directly observe kelp forests to specific kelp forests sites or areas, rather than just counties. 

This script takes a look at which individuals and organizations are represented in the survey data v. those with publicly available data on monitoring or restoration sites. 

Key sources of information:

[Sanctuary Integrated Monitoring Network Map](https://csumb.maps.arcgis.com/apps/webappviewer/index.html?id=f555c42a349444f2942900139f88fe34) from [SIMON](https://sanctuarysimon.org/tools/interactive-maps/)

[Kelp Forest Challenge](https://kelpforestalliance.com/kelp-forest-challenge)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Set up  -----------------------------------------------------------------

library(readr)
library(tidyverse) 
library(dplyr) 
library(tidyr) 
library(here)
library(magrittr)
library(janitor)
#

sn.dir <- here('confidential_data')
```

## Data

### survey 

this is the raw survey data
```{r}
dat_survey <- read_csv(here(sn.dir, "raw", "kelp_jan.9.25_copy.csv"))[-c(1,2),]
dat_survey %<>% clean_names()
```

this is the cleaned up social network
```{r}
sn <- read_csv(here(sn.dir, 'processed', 'cleaned_social_network_with_org_2025-02-28.csv'))
```

this is the cleaned up data set on the answer to the question: What are the main ways you learn about kelp forest-related issues?
```{r}
info <- read_csv(here(sn.dir, 'processed','cleaned_responseID_by_info_source_q9.csv'))
```

this is the cleaned up data set on the answer to the question: How are you involved in kelp forest-related issues?
```{r}
act <- read_csv(here(sn.dir, 'processed','kelp_by_org_by_interact_2025-02-05.csv'))
```
this is the cleaned up data set for survey respondents who work for multiple organizations
```{r}
morg <- read_csv(here(sn.dir,'processed','cleaned_multiple_orgs_2025-03-17.csv'))
```

### site data sets

these are the organizations represented in the online map data or by DISES members / partners:
```{r}
kms_map <- c('Channel Islands National Marine Sanctuary', 
             'Humboldt State University','Reef Check', 
             'Vantuna Research Group', 'Occidental College - Vantuna Research Group', 
             'California State Polytechnic University Pomona',  ## one individual who is associated with Vantuna Research Group
             'University of California Santa Barbara', 'University of California Santa Barbara - Marine Science Institute',
             'PISCO','Partnership for Interdisciplinary Studies of Coastal Oceans')

kfp_map <- c('The Nature Conservancy','Get Inspired', 'The Bay Foundation')

othr <- c('Elkhorn Slough National Estuarine Research Reserve')   # one response from Otter Research Program (sites in online report)

dises <- c('University of California Davis','University of California Santa Cruz','California State Polytechnic University Humboldt')

dises_partner <- c('California Department of Fish and Wildlife', 'Reef Check','Greater Farallones Association', 'Greater Farallones National Marine Sanctuary','Monterey Bay National Marine Sanctuary')
```


*are all response IDs / orgs in the social network in the info data frame, and vice versa?* There are many missing from the social network data frame because only those who answered question 11 (which organizations and individual operators have you worked directly with? ...) are in the social network. numbers in this script are based on the number of responses in the info data frame, and org names from a combo of the social network data frame and the survey data. 
```{r}
missing_from_sn <- info$response_id[which(!(info$response_id %in% sn$response_id))]
length(missing_from_sn)

missing_from_info <- sn$response_id[which(!(sn$response_id %in% info$response_id))]
length(missing_from_info)


# View(dat_survey %>% filter(response_id %in% missing_from_sn))
```

## Direct observers

Get a list of those who (a) directly observe and collect data, or (b) just directly observe kelp forests. These should be mutually exclusive lists.
```{r echo=FALSE}
do1 <- info %>%
  group_by(response_id) %>%
  summarise(all_info=paste(info_type,collapse=",")) %>%
  filter(grepl('I directly observe conditions', all_info) & grepl('I collect or analyze data', all_info)) %>%
  dplyr::select(response_id) %>%
  left_join(sn, by='response_id') %>%
  left_join(dplyr::select(dat_survey, response_id, recipient_first_name, recipient_last_name, q2) %>% distinct())


do2 <- info %>%
  group_by(response_id) %>%
  summarise(all_info=paste(info_type,collapse=",")) %>%
  filter(grepl('I directly observe conditions', all_info) & !(grepl('I collect or analyze data', all_info))) %>%
  dplyr::select(response_id) %>%
  left_join(sn, by='response_id') %>%
  left_join(dplyr::select(dat_survey, response_id, recipient_first_name, recipient_last_name, q2) %>% distinct())


any(do1$response_id %in% do2$response_id)

paste0('Observe and Data: ',length(unique(do1$response_id)))
paste0('Observe only: ', length(unique(do2$response_id)))
```

```{r echo=FALSE}
# ---sidebar---
do1 %<>% left_join(morg,by='response_id')
to_correct <- filter(do1, is.na(org_name) & !is.na(multi_org))
do1 %<>%
  filter(response_id != to_correct$response_id) %>%
  bind_rows(
    to_correct %>% mutate(org_name=multi_org)
  )


do2 %<>% left_join(morg,by='response_id')
to_correct <- filter(do2, is.na(org_name) & !is.na(multi_org))
```


How many organizations represented?
```{r}
paste0('Observe and Data: ',length(unique(do1 %>% filter(!is.na(org_name) & org_name != "Individual") %>% pull(org_name))))
paste0('Observe only: ', length(unique(do2 %>% filter(!is.na(org_name) & org_name != "Individual") %>% pull(org_name))))
```


How many people not working on behalf of organizations?
```{r}
paste0('Observe and Data: ',length(unique(do1 %>% filter(is.na(org_name) | org_name == "Individual") %>% pull(response_id))))
paste0('Observe only: ', length(unique(do2 %>% filter(is.na(org_name) | org_name == "Individual") %>% pull(response_id))))
```


### Observe & Data: all

Include all survey respondants who answered the question on how they get their information, including those who are not in the social network. 

#### on behalf of an org

What proportion of direct observation/data collection survey respondents are on the kelp monitoring map or in the DISES group?
```{r echo=FALSE}
do1_summary <- do1 %>% mutate(avail=ifelse(org_name %in% kms_map, 'KMS Map',
                                           ifelse(org_name %in% kfp_map, 'KelpChallenge Map',
                                                  ifelse(org_name %in% othr, 'Other Online',
                                                         ifelse(org_name %in% dises, 'DISES',
                                                                ifelse(org_name %in% dises_partner, 'DISES partner', NA))))))
```
```{r}
paste0('DISES etc. Individuals: ', length(unique(filter(do1_summary, avail %in% c('DISES','DISES partner'))$response_id)), ' (',
length(unique(filter(do1_summary, avail %in% c('DISES','DISES partner'))$response_id))/length(unique(do1_summary$response_id)),')')

paste0('DISES etc. Organizations: ',length(unique(filter(do1_summary, avail %in% c('DISES','DISES partner'))$org_name)),' (',
       round(length(unique(filter(do1_summary, avail %in% c('DISES','DISES partner'))$org_name))/length(unique(do1_summary$org_name)), 3),')')


paste0('Other covered Individuals: ',length(unique(filter(do1_summary, avail %in% c('KMS Map','KelpChallenge Map','Other Online'))$response_id)), ' (',
length(unique(filter(do1_summary, avail %in% c('KMS Map','KelpChallenge Map','Other Online'))$response_id))/length(unique(do1_summary$response_id)),')')

paste0('Other covered Organizations: ',length(unique(filter(do1_summary, avail %in% c('KMS Map','KelpChallenge Map','Other Online'))$org_name)), ' (',
       round(length(unique(filter(do1_summary, avail %in% c('KMS Map','KelpChallenge Map','Other Online'))$org_name))/length(unique(do1_summary$org_name)), 3),')')
```


Save to a spreadsheet. 
```{r}
write_csv(do1_summary %>% filter(is.na(avail)), here(sn.dir, 'processed','direct_observers_data_collection_MISSING_2025-03-05.csv'))
write_csv(do1_summary %>% filter(!is.na(avail)), here(sn.dir,'processed','direct_observers_data_collection_2025-03-05.csv'))
```



Time to work on the groups I don't have good data for.
```{r}
do1_missing <- do1_summary %>% filter(is.na(avail))
```

--Side Bar: -- Which of these organizations are *not* on the kelp monitoring/challenge map or in the DISES group?
```{r echo=FALSE}
unique(do1_missing$org_name)
```


How many individuals working on behalf of an organization *not covered above* are involved in harvesting or fishing or growing? What proportion is this of individuals in this subset, and among all individuals working on behalf of an organization?
```{r}
do1_act <- do1_missing %>% filter(!is.na(org_name) & org_name != "Individual") %>%
  left_join(dplyr::select(act,response_id,interact_type), by='response_id')

do1_harvest <- unique(do1_act %>% filter(interact_type=="Harvesting or fishing or growing") %>% pull(response_id))

length(do1_harvest)


length(do1_harvest)/length(unique(do1_act$response_id))



length(do1_harvest)/ length(unique(do1_summary$response_id))
```

Which organizations are represented by these individuals?
```{r}
unique(do1_act %>% filter(response_id %in% do1_harvest) %>% pull(org_name))
```

**Mark these individuals as 'all non-protected waters'**
```{r}
do1_missing_out <- data.frame(response_id=do1_harvest) %>%
  mutate(assign='all non-protected waters')
```


And that leaves...
```{r}
length(unique(do1_act %>% filter(!(response_id %in% do1_harvest)) %>% pull(response_id)))


length(unique(do1_act %>% filter(!(response_id %in% do1_harvest)) %>% pull(response_id)))/length(unique(do1_act$response_id))



length(unique(do1_act %>% filter(!(response_id %in% do1_harvest)) %>% pull(response_id)))/ length(unique(do1_summary$response_id))
```

What organizations do these individuals work for?
```{r}
do1_act %>% filter(!(response_id %in% do1_harvest)) %>% group_by(org_name) %>% summarise(n=length(unique(response_id)))
```

Are all of these individuals in the social network (i.e., answered question #11?) 
```{r}
length(unique(do1_act %>% filter(!(response_id %in% do1_harvest) & response_id %in% sn$response_id) %>% pull(response_id)))
```

Yes!


#### individuals

How many individuals are *not* working on behalf of an organization?
```{r warning=FALSE}
do1_individ_act <- do1_summary %>% filter(is.na(org_name) | org_name == "Individual") %>%
  filter(!(response_id %in% do1_tmp$response_id)) %>%
  left_join(dplyr::select(act,response_id,interact_type), by='response_id')

length(unique(do1_individ_act$response_id))
```

How many of these are in the social network? (i.e., filled out alters info)
```{r}
length(unique(do1_individ_act %>% filter(response_id %in% sn$response_id) %>% pull(response_id)))
```

Oh wow, ok. Not many. I'll answer the questions below first for any survey respondents, and then for those included in the social network. 

How many individuals are involved in harvesting or fishing or growing? What proportion is this of all observation/data collection individuals?
```{r}
do1_individ_harvest <- unique(do1_individ_act %>% filter(interact_type=="Harvesting or fishing or growing") %>% pull(response_id))

length(do1_individ_harvest)

length(do1_individ_harvest)/ length(unique(do1_summary$response_id))
```

Who do they work with? Some may not have provided alters.
```{r}
do1_summary %>%
  filter(response_id %in% do1_individ_harvest) %>%
  dplyr::select(response_id, org_name) %>%
  left_join(dplyr::select(dat_survey, finished, response_id, recipient_first_name, recipient_last_name) %>% distinct()) %>%
  distinct() %>%
  left_join(dplyr::select(sn, response_id, alter), by='response_id') %>%
  unite(col='recipient_name', recipient_first_name, recipient_last_name, sep=" ") %>%
  group_by(response_id, recipient_name) %>% summarise(alters=paste0(alter,collapse=', '))
```

Ok so none of them provided alters... Does that mean that 0 individuals *in the social network* are involved in harvesting or fishing or growing? 
```{r}
length(unique(do1_individ_act %>% filter(interact_type=="Harvesting or fishing or growing") %>% filter(response_id %in% sn$response_id) %>% pull(response_id)))
```


How many individuals are involved in research, or a student? What proportion is this of all observation/data collection individuals?
```{r}
do1_individ_othr <- unique(do1_individ_act %>% filter(interact_type=="Research" | interact_type=="Student") %>% pull(response_id))

length(do1_individ_othr)

length(do1_individ_othr)/ length(unique(do1_summary$response_id))
```

Who do they work with? Some may not have provided alters.
```{r}
do1_summary %>%
  filter(response_id %in% do1_individ_othr) %>%
  dplyr::select(response_id, org_name) %>%
  left_join(dplyr::select(dat_survey, finished, response_id, recipient_first_name, recipient_last_name) %>% distinct()) %>%
  filter(finished=='True') %>% distinct() %>%
  left_join(dplyr::select(sn, response_id, alter), by='response_id') %>%
  unite(col='recipient_name', recipient_first_name, recipient_last_name, sep=" ") %>%
  group_by(response_id, recipient_name) %>% summarise(alters=paste0(alter,collapse=', '))
```

What do the 5 individuals in the social network do, and who do they work with?
```{r}
do1_individ_act %>% filter(response_id %in% sn$response_id) %>% dplyr::select(response_id,interact_type) %>% distinct() %>%
  group_by(response_id) %>% summarise(interact_type=paste0(interact_type, collapse=', '))
```

```{r}
do1_individ_act %>% filter(response_id %in% sn$response_id) %>%
  filter(edge_type=='collaboration') %>%
  dplyr::select(response_id,alter) %>% distinct() %>%
  group_by(response_id) %>% summarise(alters=paste0(alter, collapse=', '))
```

Mostly Reef Check


### Observe & Data: social network

Exclude individuals who did not reply to any of the collaborate / communicate / coordinate questions.





### Just Observe


Which organizations are represented by DO2s?
```{r}
unique(do2$org_name)
```

What proportion of organizations, respondents are on the kelp monitoring map or in the DISES group?
```{r echo=FALSE}
do2_summary <- do2 %>% mutate(avail=ifelse(org_name %in% kms_map, 'KMS Map',
                                           ifelse(org_name %in% dises, 'DISES',
                                                  ifelse(org_name %in% dises_partner, 'DISES partner', NA)))) %>%
  mutate(inDO1 = ifelse((!is.na(org_name) & org_name != "Individual" & org_name %in% do1$org_name), 'y','n'))


paste0('Individuals: ',
length(unique(filter(do2_summary, !is.na(avail))$response_id))/length(unique(do2_summary$response_id)))

paste0('Organizations: ',
       round(length(unique(filter(do2_summary, !is.na(avail))$org_name))/length(unique(do2_summary$org_name)), 3))
```

What organizations are not accounted for?
```{r}
unique(do2_summary %>% filter(is.na(avail)) %>% pull(org_name))
```

What organizations that are not accounted for, are also in the DO1 group?
```{r}
unique(do2_summary %>% filter(is.na(avail)) %>% filter(inDO1=='y') %>% pull(org_name))
```

Who are the individuals?
```{r}
do2_summary %>%
  filter(is.na(avail)) %>%
  filter(is.na(org_name) | org_name=="Individual") %>%
  dplyr::select(response_id, org_name) %>%
  left_join(dplyr::select(dat_survey, finished, response_id, recipient_first_name, recipient_last_name) %>% distinct()) %>%
  filter(finished=='True') %>% distinct()
```

Who do they work with? This won't be an exhaustive list because some are missing from the social network. 
```{r}
do2_summary %>%
  filter(is.na(avail)) %>%
  filter(is.na(org_name) | org_name=="Individual") %>%
  dplyr::select(response_id, org_name) %>%
  left_join(dplyr::select(dat_survey, finished, response_id, recipient_first_name, recipient_last_name) %>% distinct()) %>%
  filter(finished=='True') %>% distinct() %>%
  left_join(dplyr::select(sn, response_id, alter), by='response_id') %>%
  dplyr::select(-finished) %>%
  unite(col='recipient_name', recipient_first_name, recipient_last_name, sep=" ")
```

Save to a spreadsheet. 
```{r}
write_csv(do2_summary %>% filter(is.na(avail)), here(sn.dir, 'processed','direct_observers_MISSING_2025-03-05.csv'))
write_csv(do2_summary %>% filter(!is.na(avail)), here(sn.dir,'processed','direct_observers_2025-03-05.csv'))
```



#### harvesting or fishing or growing

How many individuals working on behalf of an organization are involved in harvesting or fishing or growing? What proportion is this of individuals in this subset, and among all individuals working on behalf of an organization?
```{r}
do2_act <- do2_summary %>% filter(!is.na(org_name) & org_name != "Individual") %>%
  left_join(dplyr::select(act,response_id,interact_type), by='response_id')

do2_harvest <- unique(do2_act %>% filter(interact_type=="Harvesting or fishing or growing") %>% pull(response_id))

length(do2_harvest)

length(do2_harvest)/length(unique(do2_act$response_id))

length(do2_harvest)/ length(unique(do2_summary$response_id))
```
Which organizations are they working for?
```{r}
do2_summary %>% filter(response_id %in% do2_harvest) %>% dplyr::select(org_name) %>% distinct()
```

How many individuals *not* working on behalf of an organization are involved in harvesting or fishing or growing? 
```{r}
do2_act_individ <- do2_summary %>% filter(is.na(org_name) | org_name == "Individual") %>%
  left_join(dplyr::select(act,response_id,interact_type), by='response_id')

do2_harvest_individ <- unique(do2_act_individ %>% filter(interact_type=="Harvesting or fishing or growing") %>% pull(response_id))

length(do2_harvest_individ)
```


Combined with above, what proportion is this of "direct observer" individuals?
```{r}
sum(length(do2_harvest),length(do2_harvest_individ))/length(unique(do2_summary$response_id))

length(do2_harvest)/ length(unique(do2_summary$response_id))
```

#### not harvesting or fishing or growing

How many individuals working on behalf of an organization are *not* involved in harvesting or fishing or growing? 
```{r}
do2_noharvest <- unique(do2_act %>% filter(!(response_id %in% do2_harvest)) %>% pull(response_id))

length(do2_noharvest)
```
Which organizations are they working for?
```{r}
do2_summary %>% filter(response_id %in% do2_noharvest) %>% dplyr::select(org_name) %>% distinct()
```


How many individuals *not* working on behalf of an organization are *not* involved in harvesting or fishing or growing? 
```{r}
do2_noharvest_individ <- unique(do2_act_individ %>% filter(!(response_id %in% do2_harvest_individ)) %>% pull(response_id))

length(do2_noharvest_individ)
```








## Other info sources

What proportion of survey respondents in the social network aren't direct observers?
```{r}
ndo <- info %>%
  group_by(response_id) %>%
  summarise(all_info=paste(info_type,collapse=",")) %>%
  filter(!(grepl('I directly observe conditions', all_info))) %>%
  dplyr::select(response_id) %>%
  left_join(sn, by='response_id') %>%
  left_join(dplyr::select(dat_survey, response_id, recipient_first_name, recipient_last_name) %>% distinct())

length(unique(ndo$response_id)) 
length(unique(ndo$response_id)) / length(unique(info$response_id))
```

How many organizations are represented by people in this category?
```{r}
unique(ndo$org_name)
```

Do these people represent new organizations, or the same organizations as the direct observers?
```{r}
unique(ndo$org_name[which(!(ndo$org_name %in% c(do1$org_name, do2$org_name)))])
```









## Interactive: extra survey data

for individuals missing org names in the processed data
```{r}
View(filter(dat_survey, response_id=='R_20uTnIwAQ3UxMrw') %>% 
       dplyr::select(response_id,finished,recipient_last_name, recipient_first_name,q1, q2, starts_with('q3'), starts_with('q5'),starts_with('q11'), q18,email))
```


update sn
```{r}
sn %>% filter(response_id=='R_1ulIyefXrmNqx1f')
```


