---
title: "ERGM Walk through"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
---
  
**Author: M Fisher**

**Date compiled: 1/26/2025**


## Description

Use a mini kelp social network to walk through ERGMs in R, using the packages `igraph`, `sna`, and `ergm`. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
library(magrittr)
library(janitor)


library(ergm)
library(sna)
library(igraph)
```


## Network Data

### raw data

```{r cars}
kelp.net <- read_csv(here('confidential_data','kelp_jan.9.25.csv'), show_col_types = FALSE) %>%
  dplyr::select(-c(1,2)) %>%
  filter(!row_number() %in% c(1, 2)) %>%
  clean_names()

colnames(kelp.net)
```

Grab only the info needed to create our social network (individual IDs, organizations they work for, organizations they *work on programs / projects with*)
```{r}
kelp.net.sub <- kelp.net %>%
  unite(col = "org_name", c('q3_individual_1', 'q3_several_1'), sep = "", na.rm = TRUE, remove = FALSE) %>%
  dplyr::select(response_id, org_name, starts_with("q11"))

colnames(kelp.net.sub)
length(unique(kelp.net.sub$response_id))
```

Re-arrange the data to make it easier to work with.
```{r}
kelp.edges <- kelp.net.sub %>%
  pivot_longer(starts_with('q11'), names_to = 'alter_count', values_to = 'alter')

head(kelp.edges)
```

clean up the names so we don't have to deal with capitalization, spaces. 
```{r}
## 
kelp.edges %<>% mutate(alter = make_clean_names(org_name, allow_dupes = TRUE),
                       alter = make_clean_names(alter, allow_dupes = TRUE)) %>%
  
```


### subset network 

We don't need all of the network to practice ERGMs. Let's just grab most people who work in / with an organization associated with DISES, to make things simpler. *Note that some people wrote in 'dises', these responses won't be represented in this mini network. 
```{r}
keep_orgs <-  c('davis','ucd','santa_cruz', 'ucsc', 'cal_poly_humboldt','reefcheck','reef_check','gfnms')

kelpg.df <- kelp.edges %>%
  filter(grepl(paste(keep_orgs, collapse="|"), org_name)==TRUE | grepl(paste(keep_orgs, collapse="|"), alter))

dim(kelpg.df)
length(unique(kelpg.df$response_id))
```

Now, simplify the org names so they match. 
```{r}
kelpg.df %<>% mutate(alter = case_when (
  grepl(paste(keep_orgs[1:2], collapse="|"), org_name) ~ 'uc_davis',
  grepl(paste(keep_orgs[3:4], collapse="|"), org_name) ~ 'uc_santa_cruz',
  grepl(keep_orgs[5], org_name) ~ 'cal_poly_humboldt',
  grepl(paste(keep_orgs[6:7], collapse="|"), org_name) ~ 'reef_check',
  grepl(keep_orgs[8], org_name) ~ 'gfnms',
  .default=org_name
), 
alter = case_when (
  grepl(paste(keep_orgs[1:2], collapse="|"), alter) ~ 'uc_davis',
  grepl(paste(keep_orgs[3:4], collapse="|"), alter) ~ 'uc_santa_cruz',
  grepl(keep_orgs[5], alter) ~ 'cal_poly_humboldt',
  grepl(paste(keep_orgs[6:7], collapse="|"), alter) ~ 'reef_check',
  grepl(keep_orgs[8], alter) ~ 'gfnms',
  .default=alter
)
)
```

what org names are left that we might need to clean up?
```{r}
kelpg.df$org_name[which(!(kelpg.df$org_name %in% c('uc_davis','uc_santa_cruz','cal_poly_humboldt','reef_check', 'gfnms')))]
```

some final clean up...
```{r}
kelpg.df %<>% mutate(alter = case_when (
  grepl('univ_ca_santa_barbara', org_name) ~ 'uc_santa_barbara',
  grepl('sunflower_star', org_name) ~ 'sunflower_star_lab',
  grepl('urchin_commission', org_name) ~ 'ca_sea_urchin_commission',
  grepl('great_great_kelp', org_name) ~ 'giant_giant_kelp_restoration',
  grepl('giant_giant_kelp', org_name) ~ 'giant_giant_kelp_restoration',
  grepl('greater_farallones', org_name) ~ 'gfnms',
  grepl('university_of_wisconsin', org_name) ~ 'uwisc_milwaukee',
  grepl('friday_harbor', org_name) ~ 'uw_friday_harbor',
  grepl('moss_landing_marine', org_name) ~ 'sjsu_moss_landing',
  .default=org_name
))

unique(kelpg.df$org_name)
```

again for the alters ...
```{r}
unique(kelpg.df$alter[which(!(kelpg.df$alter %in% c('uc_davis','uc_santa_cruz','cal_poly_humboldt','reef_check', 'gfnms')))])
```


```{r}
kelpg.df %<>% mutate(alter = case_when (
  grepl('univ_ca_santa_barbara', alter) ~ 'uc_santa_barbara',
  grepl('sunflower_star', alter) ~ 'sunflower_star_lab',
  grepl('urchin_commission', alter) ~ 'ca_sea_urchin_commission',
  grepl('great_great_kelp', alter) ~ 'giant_giant_kelp_restoration',
  grepl(paste(c('giant_giant_kelp','g_2_kelp','g2kr'),collapse='|'), alter) ~ 'giant_giant_kelp_restoration',
  grepl('greater_farallones', alter) ~ 'gfnms',
  grepl('university_of_wisconsin', alter) ~ 'uwisc_milwaukee',
  grepl('friday_harbor', alter) ~ 'uw_friday_harbor',
  grepl('moss_landing_marine', alter) ~ 'sjsu_moss_landing',
  grepl('nature_conservancy', alter) ~ 'the_nature_conservancy',
  grepl(paste(c('sean_craig','rafael_cuevas_uribe','paul_bourdeau','csu','hsu'),collapse='|'), alter) ~ 'cal_poly_humboldt',
  grepl(paste(c('cal_seagrant', 'sea_grant'),collapse='|'), alter) ~ 'california_sea_grant',
  grepl('tristin_mc_hugh', alter) ~ 'the_nature_conservancy',
  grepl('jan_freiwald', alter) ~ 'reef_check',
  grepl('kristen_elsmore', alter) ~ 'california_department_of_fish_and_wildlife',
  grepl('tnc', alter) ~ 'the_nature_conservancy',
  grepl('ocean_science_trust', alter) ~ 'ocean_science_trust',
  grepl('rcca', alter) ~ 'rcca',
  grepl(paste(c('watermens_alliance','watermans_alliance','waterman_s_alliance'),collapse='|'), alter) ~ 'watermens_alliance',
  grepl('watermans_alliance', alter) ~ 'watermens_alliance',
  grepl('girl_scouts_of_america', alter) ~ 'girl_scouts_of_america',
  grepl('surfrider', alter) ~ 'surfrider',
  grepl('monterey_bay_aquarium', alter) ~ 'monterey_bay_aquarium',
  grepl('sea_ranch_association', alter) ~ 'sea_ranch_association',
  grepl('surfrider', alter) ~ 'surfrider',
  grepl(paste(c('hughes','sonoma_state'), collapse='|'), alter) ~ 'sonoma_state_university',
  grepl('ucsb', alter) ~ 'uc_santa_barbara',
  grepl('mbnms', alter) ~ 'noaa_monterey_bay_national_marine_sanctuary',
  grepl('dan_abbott', alter) ~ 'reef_check',
  grepl(paste(c('urchin_diver','commercial_divers'),collapse='|'), alter) ~ 'commercial_urchin_divers',
  .default=alter
))

unique(kelpg.df$alter)
```

ok, final clean up-- just remove some edges
```{r}
kelpg.df %<>% filter(!(alter %in% c('di_ses_ppl','kelp_rises_personnel','na','x')) & !(grepl('mermaid',alter)))

kelpg.df %<>% mutate(alter=ifelse(alter=='the_cher_ae_heights_indian_community_of_the_trinidad_rancheria',
                                  'the_cherAe_heights_indian_community_of_the_trinidad_rancheria', alter))

unique(c(kelpg.df$alter,kelpg.df$org_name))
```

yay! 

## Create graph

Un-weighted, directed `network` object
```{r}
kelpg.df %>%
  mutate(org_name=ifelse(org_name=='x', response_id, org_name)) %>%
  dplyr::select(org_name, alter) %>%
  distinct() %>%
  filter(org_name != alter) %>%
  distinct() %>%
  as.network(directed=TRUE) -> kelp.g

class(kelp.g)
```

There doesn't appear to be a way to create a weighted network? There is in igraph...
```{r}
kelp.wg.df <- kelpg.df %>%
  mutate(org_name=ifelse(org_name=='x', response_id, org_name)) %>%
  group_by(org_name, alter) %>%
  summarise(n=n()) %>%
  filter(org_name != alter)

kelp.wg <- igraph::graph_from_edgelist(as.matrix(kelp.wg.df[,1:2]), directed=TRUE)

E(kelp.wg)$weight <- kelp.wg.df$n

class(kelp.wg)
```
save an image of our mini network
```{r}
png(here('scripts','00_ergm_walkthrough.png'))
plot(kelp.wg, l=layout_with_fr(kelp.wg))
dev.off()
```


## ERGM walkthrough

### Part 1. 


